\phantomsection\addcontentsline{toc}{section}{Literaturverzeichnis}
\section*{Literaturverzeichnis}

\begingroup\setlength{\parindent}{0pt}\setlength{\parskip}{0.5em}

\noindent\hangindent=1.5em Adolfsson, J./Saleh, D. (2026): Analyzing Order-to-Cash Using Process Mining. A Case Study in Collaboration with Paulig, Master's Thesis, Department of Technology Management and Economics, Chalmers University of Technology, Gothenburg.\par

\noindent\hangindent=1.5em Berti, A./van Zelst, S. J./van der Aalst, W. M. P. (2019): Process Mining for Python (PM4Py). Bridging the Gap Between Process- and Data Science, in: ICPM Demo Track 2019, CEUR Workshop Proceedings, Bd. 2374.\par

\noindent\hangindent=1.5em Coletta, S. (2026a): ERP-Systeme. Vorlesungsunterlagen vom 03.03.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026b): ERP-Systeme. Vorlesungsunterlagen vom 10.03.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026c): ERP-Systeme. Vorlesungsunterlagen vom 28.04.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026d): ERP-Systeme. Vorlesungsunterlagen vom 05.05.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026e): ERP-Systeme. Vorlesungsunterlagen vom 19.05.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026f): ERP-Systeme. Vorlesungsunterlagen vom 02.06.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026g): ERP-Systeme. Vorlesungsunterlagen vom 09.06.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026h): ERP-Systeme. Vorlesungsunterlagen vom 23.06.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026i): ERP-Systeme. Vorlesungsunterlagen vom 30.06.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Coletta, S. (2026j): ERP-Systeme. Vorlesungsunterlagen vom 14.07.2026, FOM Hochschule für Oekonomie \& Management, Essen, Sommersemester 2026.\par

\noindent\hangindent=1.5em Gronau, N. (2014): Enterprise Resource Planning. Architektur, Funktionen und Management von ERP-Systemen, 3. Aufl., De Gruyter Oldenbourg, Berlin/München.\par

\noindent\hangindent=1.5em IEEE (2016): IEEE Standard for eXtensible Event Stream (XES) for Achieving Interoperability in Event Logs and Event Streams, IEEE Std 1849-2016, IEEE, New York.\par

\noindent\hangindent=1.5em Leemans, S. J. J./Fahland, D./van der Aalst, W. M. P. (2013): Discovering Block-Structured Process Models from Event Logs. A Constructive Approach, in: Colom, J.-M./Desel, J. (Hrsg.): Application and Theory of Petri Nets and Concurrency, LNCS 7927, Springer, Berlin/Heidelberg, S. 311--329.\par

\noindent\hangindent=1.5em Nadukuru, S./Dandu, M. M. K./Balasubramaniam, V. S./Renuka, A./Goel, O. (2024): Enhancing Order to Cash Processes in SAP Sales and Distribution, in: Darpan International Research Analysis, 12. Jg., Nr. 1, S. 108--139.\par

\noindent\hangindent=1.5em Peters, R./Nauroth, M. (2019): Process-Mining. Geschäftsprozesse: smart, schnell und einfach, Springer Gabler, Wiesbaden.\par

\noindent\hangindent=1.5em Reinkemeyer, L. (Hrsg.) (2020): Process Mining in Action. Principles, Use Cases and Outlook, Springer, Cham.\par

\noindent\hangindent=1.5em Rozinat, A./van der Aalst, W. M. P. (2008): Conformance Checking of Processes Based on Monitoring Real Behavior, in: Information Systems, 33. Jg., Nr. 1, S. 64--95.\par

\noindent\hangindent=1.5em SAP AG (2013): Sales -- A/R. Sales Order to Cash, Schulungsunterlage TB1000 (SAP Business One, Version 9.0), SAP AG, Walldorf.\par

\noindent\hangindent=1.5em SAP SE (2022): Sample Content for Process Mining on SAP S/4HANA -- Order to Cash. Processes and Functions supporting Sample Business Scenarios, SAP Profitability and Performance Management, Dokumentversion 3.0 SP20 (2022-12-20), SAP SE, Walldorf.\par

\noindent\hangindent=1.5em Scheibler, J. (2021): Vertrieb mit SAP S/4HANA. Das Praxishandbuch, Rheinwerk, Bonn.\par

\noindent\hangindent=1.5em van der Aalst, W. M. P. (2016): Process Mining. Data Science in Action, 2. Aufl., Springer, Berlin/Heidelberg.\par

\noindent\hangindent=1.5em van der Aalst, W. M. P. (2019): Object-Centric Process Mining. Dealing with Divergence and Convergence in Event Data, in: Ölveczky, P. C./Salaün, G. (Hrsg.): Software Engineering and Formal Methods (SEFM 2019), LNCS 11724, Springer, Cham, S. 3--25.\par

\noindent\hangindent=1.5em van der Aalst, W. M. P. et al. (2012): Process Mining Manifesto, in: Daniel, F./Barkaoui, K./Dustdar, S. (Hrsg.): Business Process Management Workshops (BPM 2011), LNBIP 99, Springer, Berlin/Heidelberg, S. 169--194.\par

\noindent\hangindent=1.5em van der Aalst, W. M. P./Weijters, A. J. M. M./Măruşter, L. (2004): Workflow Mining. Discovering Process Models from Event Logs, in: IEEE Transactions on Knowledge and Data Engineering, 16. Jg., Nr. 9, S. 1128--1142.\par

\noindent\hangindent=1.5em van Dongen, B. F. (2019): BPI Challenge 2019. Event Log, 4TU.ResearchData, Eindhoven.\par

\noindent\hangindent=1.5em Weijters, A. J. M. M./van der Aalst, W. M. P. (2003): Rediscovering Workflow Models from Event-Based Data Using Little Thumb, in: Integrated Computer-Aided Engineering, 10. Jg., Nr. 2, S. 151--162.\par



\endgroup
